---
title: "Cabbages"
author: "Marcia Alarcon"
date: "16 September 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference in the amount of Vitamin C content of cabbages cultivated with methods c39 and c52.

$H_A$: There is a difference in the Vitamin C content based on cultivation method.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

VitC is a numerical variable. Cult is a categorical variable.So we need the helper file numerical~Cat. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

This plot shows that in vitamin c cultivated with the content c39 is less effective then those cultivated with c52 content. The bottom of the barrel that contains vitamin c cultivated in c52 box is above the barrel for those with the vitamin c cultivated with c39 content.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

This table shows that the content of vitamin c cultivated in with the method c39 average is 52 and the average content cultivated with c52 is 64.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The p value is 0.00000003405 which is smaller than 0.05. There is a difference between the vitamin c content cultivated with c52 than in c39. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question is there a difference in the amount of Vitamin C content of cabbages based on cultivation methods c39 and c52. The boxplots show that there is a difference. The numerical summary showed the difference of c52 resulted in 13 more IUs. According to the research and the plots provided with the evidence of p value equaling to 0.00000003405 which is a very small number. This means that if the null hypothesis were true the likelihood of getting the result we found is so small that I reject the null hypothesis.